BioTime

### 2019-05-15 biotime.Rmd
clean up synonym resolutions, fix the join.

#match all the un-ID'd names to other providers, check if synonyms given by those providers match known ITIS species 
syn_res <- bind_rows(synonyms(biotime_data %>% filter(is.na(id)) %>% pull(matchingName) %>% unique(), "ott"),
                  synonyms(biotime_data %>% filter(is.na(id)) %>% pull(matchingName) %>% unique(), "gbif"),
                  synonyms(biotime_data %>% filter(is.na(id)) %>% pull(matchingName) %>% unique(), "col"),
                  synonyms(biotime_data %>% filter(is.na(id)) %>% pull(matchingName) %>% unique(), "ncbi"),
                  synonyms(biotime_data %>% filter(is.na(id)) %>% pull(matchingName) %>% unique(), "wd"),
                  synonyms(biotime_data %>% filter(is.na(id)) %>% pull(matchingName) %>% unique(), "iucn")
                  ) %>%
  pull(synonym) %>% 
  na.omit() %>% 
  unique() %>%
  by_name("itis") %>%
  select(id = acceptedNameUsageID, input, scientificName) %>% 
  drop_na(id) %>% 
  left_join(data %>% select(-species, -genus), by = c("input" = "genus_species")) %>%
  rename(matchingName = input)

@@

#These two should be equal, why aren't they??
dim(syn_res)  
biotime_data %>% filter(matchingName %in% syn_res$matchingName) %>% dim()
biotime_data %>% filter(is.na(id)) %>% dim()
```

>>>>

unmatched <- biotime_data %>% filter(is.na(id)) %>% pull(matchingName) %>% unique()
providers <- c("ott", "gbif", "col", "ncbi", "wd", "iucn")

#match all the un-ID'd names to other providers, check if synonyms given by those providers match known ITIS species 
alt_names <- map_df(providers, function(name) synonyms(unmatched, name)) %>%
  drop_na(acceptedNameUsageID)

syn_res <- bind_rows(by_name(na.omit(unique(alt_names$synonym)),"itis"),
                     by_name(na.omit(unique(alt_names$acceptedNameUsage)),"itis")) %>%
  select(id = acceptedNameUsageID, input, scientificName) %>% 
  drop_na(id) %>% 
  distinct() %>%
  inner_join(data %>% select(-species, -genus), by = c("input" = "genus_species"), na_matches =  "never") %>%
  rename(matchingName = input)

@@

# #These two should be equal, why aren't they??
# dim(syn_res)  
# biotime_data %>% filter(matchingName %in% syn_res$matchingName) %>% dim()
# biotime_data %>% filter(is.na(id)) %>% dim()
```
